**Bayesian statistics for longitudinal studies in biomedical research**

### 2020-10-22 Manuscripts/Manuscript_AM_v1.Rmd
Updated figure

bibliography: refs.bib
output:
  word_document:
    reference_docx: docx_template.docx
  pdf_document: default
  css: style.css
  html_document: default
mainfont: Times New Roman
link-citations: yes
subtitle: '_Their application and use in biomedical research_'
biblio-style: apalike
---

@@

```{r,FIGURE 1,echo=FALSE, message=FALSE, warning=FALSE}
rm(list=ls())
set.seed(123)
library(ggplot2)
library(splines)
library(tidyverse)
library(here)

>>>>

bibliography: refs.bib
output:
  pdf_document: 
    fig_caption: yes
  html_document: default
  css: style.css
  word_document:
    reference_docx: docx_template.docx
mainfont: Times New Roman
link-citations: yes
subtitle: '_Their application and use in biomedical research_'
biblio-style: apalike
---

@@

```{r,FIGURE 1,echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Simulated longitudinal data with a linear trend.'}
rm(list=ls())
set.seed(123)
library(ggplot2)
library(splines)
library(tidyverse)
library(here)
